---
title: "Eating Out"
author: "Lisa Davis"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

In this data analysis, we will be analyzing the difference in what race eats out more among whites, blacks and others.

## There were two years in which the General Social Survey asked about the frequency of eating out.
### Find those years and for the first year the question was asked download that years data in a stata format - its name will be "GSSxxxx.dta" where the xxxx is replaced by the year.  For example if the year was 1983 its name would be GSS1983.dta. Your assignment is to download the GSS yearly dataset for the first year the question was asked and then  write up the answer to the question by editing the  code block in line 31 to eval=TRUE and finish the job. 

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
```
```{r, eval=TRUE, include=F}
GSS <-readstata13::read.dta13(file="GSS1996.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```


# Method

The variables of the problem is cat~num, in order to determine which ethnicity eats out more. The cat represents the race and num represents the amount.


# Discriptive Results


The graph shows what race eats out more than the other.

## graphical results


The results is explained on the barchart.


```{r}
barchartGC(~race + eatout,data=mydata)
barchartGC(~race + eatout,data=mydata,type="percent")

```

The graphs suggest that there is a difference in which race eats out more. The graph suggest that the whites eats out more than the blacks and others.


## Numerical discriptive results

```{r}
table1 <- xtabs(~race + eatout, data=mydata)
rowPerc(table1)
colPerc(table1)
```

The numerical discriptive results shows that the frequency of whites ethnicity, eats out more than blacks and other ethnicity. 

### Inferential results

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisherXY(mydata$race,mydata$eatout,printAll=T)
```


Chi square test shows the p value 0.0008179, the number is so small, we reject the null hypothesis. The fisher exact test shows the p value is 0.001208 is also too small, so we reject the null hypothesis. There is a difference in eating out with whites and blacks. whites eat out more than blacks, there's no difference in other ethnicity.
The fisher exact test shows the p value is 0.0008179
The fisher xy test shows that the p value is 0.2815

### Discussion and conclusion

Based on the results, considering the P value 0.0008179 is so small, i rejected the null hypothesis. Therefore there is a difference in frequency of eating out between the white ethnic group and eating out. The difference in frequency is between whites and others,but there is no difference between whites and others, and there is no difference between black and others. The whites ethnic groups eats out more than blacks and others ethnic groups.
The fisher xy test shows that the p value is 0.2815
